---
title: "Draft Quarto document"
author: "Oliver"
format: html
---

## Header 1

```{r setup}
#| include: false


library(tidyverse)
library(here)
library(fs)
# library(snakecase) # inside this package is a function that can help turn column names into "snakecase" -> used in the read function we made
source(here("R/functions.R"))
```


## Importing new data

name_repair = to_snake_case = helps convert the column names to snakecase (better for readability)

n_max is used to tell how many rows to import. might be useful for larger dataset to get a view of the data
```{r}
#| eval: false
# Code chunk

here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```

## Exercise: Reading other files

```{r}
#| eval: false
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    # n_max = 100
  )

here("data-raw/nurses-stress/stress/6B/6B_1587585327/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```


## Making a function to add numbers

```{r}
#' Add two numbers together
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of two numbers
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}
```


## create a function to import data

```{r}
#| eval: false
#' Read in nurses' stress data file
#'
#' @param file_path this is the oath to a data file
#' @param max_rows this is the number of rows shown in the output. Default 100
#'
#'
#' @returns outputs a dataframe/tibble
read <- function(file_path, max_rows = 100) {
  data <- file_path %>%
    readr::read_csv( # to explicitly tell R studio to use read_csv from readr package
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = max_rows
    )
  return(data)
}
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read()
```

```{r}
# Outputs only 100 rows (default)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read(max_rows = Inf)
```


## using map()

```{r}
#| eval: false
hr_files <- here("data-raw/nurses-stress/") %>%
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE)

hr_files

hr_data <- hr_files %>%
  map(read) %>% # here we use the read function we made but without BRACKETS ()
  list_rbind(names_to = "file_path_id") # use rbind because columns names are the same for the different files


hr_data
```


## Exercise: Convert map to function and use on sleep

```{r}
#| eval: false
#' Read_all ".csv.gz" files in the stress/ folder into one data frame
#'
#' @param filename give the filename we want to read in
#' @param max_rows specify the number of rows it should load in
#'
#' @returns returns a table consisting of all files with the filename given as input

read_all <- function(filename, max_rows = 5) {
  files <- here::here("data-raw/nurses-stress/") %>%
    fs::dir_ls(regexp = filename, recurse = TRUE)

  data <- files %>%
    purrr::map(read, max_rows) %>%
    purrr::list_rbind(names_to = "file_path_id")

  return(data)
}


read_all("HR.csv.gz", max_rows = 2)
```


## Inspecting the data

```{r}
hr_data <- read_all("HR.csv.gz")

survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()

hr_data
survey_data
```

## using regex for ID

```{r}
hr_data %>%
  mutate(
    id = str_extract(
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) %>%
      str_remove("/stress/") %>%
      str_remove("/"),
    .before = file_path_id # this argument in mutate is used to add the new column before the "file_path_id" column
  ) %>%
  select(-file_path_id)
```


```{r}
#| eval: false
#' get_participant_id function to get participant id extracted
#'
#' @param data input the data that needs to have ID extracted
#'
#' @returns A data frame with a new column with ID extracted file_path_id removed
get_participant_id <- function(data) {
  data_id <- data %>%
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        pattern = "(?<=/stress/)[:alnum:]{2}(?=/)"
      ),
      .before = file_path_id # this argument in mutate is used to add the new column before the "file_path_id" column
    ) %>%
    dplyr::select(-file_path_id)

  return(data_id)
}
```

## working with across()

```{r}
hr_data <- read_all("HR.csv.gz") %>%
  get_participant_id()

hr_data
```



functions inside a functions do not have (). see below with is.numeric as function

```{r}
hr_data %>%
  summarise(across(where(is.numeric), list(
    mean = mean,
    meadian = median,
    sd = sd,
    minimum = min,
    maximum = max
  )))
```


## Working with dates

```{r}
hr_data %>%
  mutate(
    datetime = lubridate::round_date(collection_datetime,
      unit = "minute"
    ),
    .before = collection_datetime
  )
```

## Summarising by groups

```{r}
hr_data %>%
  mutate(
    collection_datetime = lubridate::round_date(collection_datetime,
      unit = "minute"
    )
  ) %>%
  summarise(
    across(
      where(is.numeric),
      list(
        mean = mean,
        sd = sd,
        median = median
      )
    ),
    .by = c(id, collection_datetime)
  )
```



## Exercise 20.6
To move a package to depends in the DESCRIPTION use:
usethis::use_package("tidyselect", type = "Depends")
```{r}
#| eval: false

#' summarised_data a function to summarise data by datetime
#'
#' @param data a data frame
#'
#' @returns a data with new collumns of mean, sd, and median per minute

summarise_by_datetime <- function(data) {
  summarised_data <- data %>%
    dplyr::mutate(
      collection_datetime = lubridate::round_date(collection_datetime,
        unit = "minute"
      )
    ) %>%
    dplyr::summarise(
      dplyr::across(
        tidyselect::where(is.numeric),
        list(
          mean = mean,
          sd = sd,
          median = median
        )
      ),
      .by = c(id, collection_datetime)
    )

  return(summarised_data)
}
```


```{r}
#| eval: false


#' read_sensor_data a function to import sensor data from the nurses
#'
#' @param filename The filename for the data to be imported
#'
#' @returns a dataframe with summarised data

read_sensor_data <- function(filename, max_rows = 100) {
  data <- read_all(filename, max_rows = max_rows) %>%
    get_participant_id() %>%
    summarise_by_datetime()
  return(data)
}
```

## Pivot longer

```{r}
# reading in the survey data
survey_data <-
  here("data-raw/nurses-stress/survey-results.csv.gz") %>%
  read()

#
survey_data
```

```{r}
survey_tidy <- survey_data %>%
  mutate(
    date = lubridate::mdy(date),
    start_datetime = lubridate::as_datetime(paste(date, start_time)),
    end_datetime = lubridate::as_datetime(paste(date, end_time)),
    datetime_id = start_datetime,
    .before = start_time
  ) %>%
  select(-c(date, start_time, end_time, duration))
```

```{r}
survey_tidy %>%
  select(id, datetime_id, start_datetime, end_datetime) %>%
  pivot_longer(
    c(
      start_datetime,
      end_datetime
    ),
    names_to = NULL, # this removes the default column "name" that pivot_longer creates
    values_to = "collection_datetime"
  ) %>%
  group_by(pick(-collection_datetime)) %>%
  complete(
    collection_datetime = seq(
      min(collection_datetime),
      max(collection_datetime),
      by = 60
    )
  ) %>%
  ungroup()
```





## Exercise 21.4
```{r}
#| eval: false
#' tidy_survey_dates to tidy the survey data dates
#'
#' @param data survey data
#'
#' @returns a tidied dataframe with tidied and correct dates
tidy_survey_dates <- function(data) {
  tidied <- data %>%
    dplyr::mutate(
      date = lubridate::mdy(date),
      start_datetime = lubridate::as_datetime(paste(date, start_time)),
      end_datetime = lubridate::as_datetime(paste(date, end_time)),
      datetime_id = start_datetime,
      .before = start_time
    ) %>%
    dplyr::select(-c(date, start_time, end_time, duration))

  return(tidied)
}
```

```{r}
#| eval: false
#' survey_to_long a function that formats data into long format
#'
#' @param data insert tidied survey datetime data
#'
#' @returns returns the survey data in a long format
survey_to_long <- function(data) {
  longer <- data %>%
    dplyr::select(id, datetime_id, start_datetime, end_datetime) %>%
    tidyr::pivot_longer(
      dplyr::ends_with("_datetime"),
      names_to = NULL, # this removes the default column "name" that pivot_longer creates
      values_to = "collection_datetime"
    ) %>%
    dplyr::group_by(dplyr::pick(-collection_datetime)) %>%
    tidyr::complete(
      collection_datetime = seq(
        min(collection_datetime),
        max(collection_datetime),
        by = 60
      )
    ) %>%
    dplyr::ungroup()


  return(longer)
}
```

## Joining datasets

```{r}

survey_long %>% 
  left_join(survey_tidy)
survey_data
#this gives an error about unexpected matches which should make one look in to the data

survey_tidy %>% 
  count(id, datetime_id) %>% 
  filter(n > 1)
#this shows that some id have multiple counts, something that should make one go into documentation of the data
  #the logical explanation here might be that it is a data entry error


survey_long %>% 
  right_join(survey_tidy)


survey_long %>% 
  full_join(survey_tidy)


nrow(full_join(survey_long, survey_tidy))

```


```{r}

nurses_stress <- survey_long %>% 
  full_join(survey_tidy) %>% 
  full_join(hr_data)

nurses_stress %>% 
  arrange(id, collection_datetime) %>% 
  view()


```


